\documentclass[12pt]{article}
\usepackage{graphicx, hyperref}

\title{Collection of Copyright and Design}
\author{Hakim Yusuf}
\date{2026}

\begin{document}
\maketitle

\newpage
\tableofcontents

\newpage
\section{Introduction}

Presentation communicates messages that showcase the meaning we need, whether the meaning is logical or emotional. Anyone can look at a newspaper and predict where the stock market can lead, using logic of current affairs on where resources will be placed, which says more about what the economy is about to do through trade deals or conflict that leads to tariffs. Another person can look at the same paper that predicts how people will struggle or benefit from these trade deals. The point is the narrative of communication to express how situations will occur. The internet is now providing all the information there is, we can find as well as false reports. The act of copywriting is an active battle of understanding where the readers need to know and feel.

\section{Personal Life}

I am Hakim Yusuf, an aspiring Software Engineer who would consider myself a polymath, as the saying goes, I am \textit{"a master of none"}. I have always been adaptable, that lead to me earning many skills. I will admit the skills I gained, I often drop as I get good or just bored with repeats, but I will not do so in my career, as of course I need to make a living, so why not try out one of my hobbies as a career, which led me to the IT field. It bridges the gap for me of being scientific and creative. I would love to apply my other hobbies to this as well. I have had IT as a hobby for a while now. I remember using \textbf{Linux} for the first time back in 2017, using \textbf{Kali Linux} with a live USB boot drive on my 8th-gen \textbf{Intel Celeron} laptop. I was in \textit{Grade 9} at the time of using it and everything felt better with \textbf{Linux} running smoothly on my weak laptop. Daily driving \textbf{Linux} was never an option due to \textbf{Adobe} and \textbf{Microsoft Office} holding me back, yet live USB was so useful as I just worked on \textbf{Linux} then saved files on my \textit{C: Drive}. \\

\textbf{Linux} introduced me to the \textit{Open Source Community} that has led me to be grateful to all the developers who built software for people to use without an subcription plan to hassle them about. I would like to develop code soon for the community, but I have yet to build my passion projects to get better at programming and build software I would use everyday so maybe I can share and help those who can benefit from them. If you are wondering what distro I am using, I am just using \textbf{Debian Linux} on \textbf{Windows Subsystem for Linux (WSL)} as I still need \textbf{Windows}. I just finished and am awaiting graduation, so daily driving \textbf{Linux} might be an option now since I could just use Office 365 online for future work. The only problem is anti-cheat, as it is not friendly with \textbf{Linux}, so it won't work out unless I just dual-boot, which I have done before with issues, which is why I am still using \textbf{WSL}. I play a game called \textbf{Valorant}, which is a first-person shooter game with anti-cheat called \textbf{Vanguard} that will not work on \textbf{Linux}. I will wrap it here, I am just a technical and creative person who just enjoys how complicated system works, not just in IT that can fit in any environment.

\newpage
\section{Copywriting}
Now that I have introduced myself, these projects will show the skills I have gained that I have done for my modules at \textbf{Eduvos} in terms of design and copywriting.

\subsection{\LaTeX Skills}
There are two \LaTeX files showing the use cases of \LaTeX I was assigned to do.\\

Click below:\\
\href{https://github.com/hakimyusuf48/Collection-of-Copyright-and-Design/blob/main/LaTex/LaTex_1.tex}{\LaTeX 1} \\
\href{https://github.com/hakimyusuf48/Collection-of-Copyright-and-Design/blob/main/LaTex/LaTex_2.tex}{\LaTeX 2}


\subsection{Blog Project}

This website showcase capabilities of blogging and maintaining a good website using \textbf{Wix.com} to host, where the content will be held with interesting stories I was reading at that time.\\

Click Here: \\
\href{https://con-1085478-z6h4.wixsite.com/thelinuxblog}{The Linux Blog}\\

\subsection{Figma Project}
This project is supposed to showcase good design UI from the \url{https://arngren.net} to the Figma design you can find in the files on GitHub.\\

Click below:\\
\href{https://github.com/hakimyusuf48/Collection-of-Copyright-and-Design/blob/main/Figma/arngren_wireframe.fig}{WireFrame} \\
\href{https://github.com/hakimyusuf48/Collection-of-Copyright-and-Design/blob/main/Figma/arngren.fig}{UI Design}

\newpage
\section{Contacts}
\begin{itemize}
    \item \href{www.linkedin.com/in/hakim-yusuf-68211b271}{LinkedIn}
    \item \href{https://github.com/hakimyusuf48}{GitHub}
\end{itemize}

\end{document}
